Deep Neural Architectures for Discourse Segmentation in E-Mail Based Behavioral Interventions

### 2018-11-16 paper-amia-summit-2019/manuscript.tex
update response to reviewers and manuscript

\begin{table}[ht]
\centering
\caption{\textbf{\hl{Summary of experimental dataset}}}
\label{tab:datastat}
 \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
  \hline
   \multirow{2}{*}{\textbf{Sessions}} & \multirow{2}{*}{\textbf{Instances}} & \multicolumn{2}{|c|}{\textbf{Class Segments}} & \multicolumn{2}{|c|}{\textbf{Tokens}} & \multicolumn{2}{|c|}{\textbf{Emails}} & \multicolumn{2}{|c|}{\textbf{Annotation}} \\\cline{3-10}
   &  & \textbf{new}  & \textbf{same} & \textbf{word} & \textbf{punctuation}  & \textbf{patient} & \textbf{provider} & \textbf{method}  & \textbf{codes} \\ \hline    
 49 & 102,917 & 3,138 & 99,779 & 95,777 & 7,140 & 281 & 330 & MYSCOPE & 115 \\ \hline
  \end{tabular}
\end{table}

@@

Punctuation mark and POS features resulted in significant improvement in the performance of machine learning and all deep learning methods. Especially, punctuation features have the higher individual impact on model performance compared to POS features. \hl{In all cases, CRF and MLP methods performed better, when word embeddings are used in conjunction with punctuation and POS features. Punctuation features improved the performance of BRNN and CRNN while POS features lowered their AUPR values. We believe that the BRNN and CRNN performed poorly with POS features because POS tagging is a supervised learning solution that uses features like the previous word and next word. Since we already considered neighbor words by utilizing bi-directional RNN, it failed to achieve good results with redundant information. We observed that MLP achieved highest precision which may be related to the fact that MLP poorly learned ``new segment'' and misclassiified new segment words as same segment in 30\%-40\% of the time.}

>>>>

\begin{table}[ht]
\centering
\caption{\textbf{\hl{Summary of the experimental dataset}}}
\label{tab:datastat}
 \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
  \hline
   \multirow{2}{*}{\textbf{Sessions}} & \multirow{2}{*}{\textbf{Instances}} & \multicolumn{2}{|c|}{\textbf{Class Segments}} & \multicolumn{2}{|c|}{\textbf{Tokens}} & \multicolumn{2}{|c|}{\textbf{Emails}} & \multicolumn{2}{|c|}{\textbf{Annotation}} \\\cline{3-10}
   &  & \textbf{new}  & \textbf{same} & \textbf{word} & \textbf{punctuation}  & \textbf{patient} & \textbf{provider} & \textbf{method}  & \textbf{codes} \\ \hline    
 49 & 102,917 & 3,138 & 99,779 & 95,777 & 7,140 & 281 & 330 & MYSCOPE & 115 \\ \hline
  \end{tabular}
\end{table}

@@

Punctuation mark and POS features resulted in significant improvement in the performance of machine learning and all deep learning methods. Especially, punctuation features have the higher individual impact on model performance compared to POS features. \hl{In all cases, CRF and MLP methods performed better, when word embeddings are used in conjunction with punctuation and POS features. Punctuation features improved the performance of BRNN and CRNN while POS features lowered their AUPR values. We believe that the BRNN and CRNN performed poorly with POS features because POS tagging is a supervised learning solution that uses features like the previous and next word. Since we already considered neighbor words by utilizing bi-directional RNN, it failed to achieve good results with redundant information. We observed that MLP achieved the highest precision which may be related to the fact that MLP poorly learned ``new segment'' and misclassified new segment words to same segments in 30\%-40\% of the time.}
